---
author: Eric Zhao
bibliography: references.bib
date: "`r format(Sys.time(), '%d %B %Y')`"
title: "**Two Variable Data Analysis**"

CJKmainfont: IPAPMincho
csl: chicago.csl
fontsize: "10pt"
geometry: margin=2cm
header-includes:
  - \usepackage{nonfloat}
  - \usepackage{multicol}
  - \newcommand{\hideFromPandoc}[1]{#1}
  - \hideFromPandoc{
      \let\Begin\begin
      \let\End\end
    }
  - \raggedcolumns
indent: True
linestretch: 1
link-citations: True
numbersections: True
output:
  pdf_document:
    df_print: kable
    fig_width: 6
    fig_height: 4
    fig_crop: False
    highlight: monochrome
    keep_tex: True
    latex_engine: xelatex
toc: True
---

```{r global_options, include=FALSE}
extrafont::loadfonts()
fulldata <- readr::read_csv("data.csv")
data <- readr::read_csv("sample.csv")
data <- data[order(data$Season), ]
par(mar = c(2, 3, 0, 3), oma = c(0, 0, 0, 0), family = "CM Roman CE")
score <- data$Score
season <- data$Season

knitr::knit_hooks$set(wrapf = function(before, options, envir) {
  if (before) {
    return("\\begin{minipage}{0.85\\columnwidth}\n\\mbox{}\n\\centering")
  } else {
    output <- vector(mode = "character", length = options$fig.num + 1)

    for (i in 1:options$fig.num) {
      output[i] <- sprintf("\\includegraphics{%s}\n\\figcaption{%s}",
                           knitr::fig_path(number = i), options$fig.cap)
    }

    output[i + 1] <- "\\end{minipage}\\bigskip"
    return(paste(output, collapse = ""))
  }
})
```

\medskip
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.2pt}}

\Begin{multicols}{2}

# Introduction

This report attempts to analyze the correlation between time, measured by the number of
cours since the first cour of 1980, and the score of anime, gathered from the anime
database and community website, [MyAnimeList.net](https://myanimelist.net).

## Background

「アニメ」, romanized in the Hepburn system (a system for the romanization of Japanese
using the Latin alphabet [@ref_romanization_sys]) as "anime", is defined in the
Merriam-Webster English Dictionary as "a style of animation originating in Japan that is
characterized by stark colorful graphics" [@ref_anime_def]. Some scholars suggest that it
may not appropriate to refer to "anime" narrowly as an art style, but rather generally as
animation created by Japanese artists within a Japanese context
[@ref_anime_cross_culture]. In general usage, the word may be used to refer to a single
production, a plural number of productions, or the medium as a whole. In this study, the
word "show" may also be used to refer to a single anime production.

There is no single definition of which productions may be classified as "anime" because
the meaning of the word in the Japanese language describes all forms of animated media.
Some scholars suggest that the term can be used to refer not only to animation from Japan,
but also animated media from other nations. Others strictly limit the classification of
anime to only Japanese animation.

Discussion has been published regarding effect of anime consumption by international
audiences in amplifying understanding and consideration across cultures
[@ref_anime_cross_culture]. Price discusses how exposure to anime internationally has
sparked and furthered cross-cultural interest. With the expansion of the internet, access
and exposure to anime has increased, and many websites have developed as hubs for the
gathering of millions of viewers across the globe.

One such website, MyAnimeList.net (referred subsequently as simply "MyAnimeList"), is an
English-speaking anime and manga database and community founded in 2006 by Garrett Gyssler
[@ref_mal_founded]. The website maintains a database of professionally produced animation
from Japan, Korea, China, or a mixture of those three nations. Independent works may be
added if they pass certain qualifications. The database does not include live-action
productions, trailers or advertisements, foreign versions of anime, or titles that have
not been confirmed to exist [@ref_mal_db_guidelines]. The anime in the MyAnimeList are the
anime considered in this study.

The database contains a wide variety of information on each title, including synopses,
background information, the genres of entertainment it might be considered to belong to,
information about the producing studio(s) and domestic and international licensors,
official artwork, per-episode information.

A particular property of interest is the "season" the anime first premiered in. In
consideration of TV anime releases, the term "season" or "cour" may be used in reference
to approximately a single quarter, or thirteen weeks, of the year. The quarters correspond
in general timing and name to the four natural temperate seasons. Most TV anime follow the
schedule of weekly releases beginning on the first or second week of the season. The
Winter season corresponds with the months of January, February, and March; the Spring
season corresponds with April, May, and June; and so on. For example, Winter 2020 began
shortly after the New Year in the first week of January 2020. All one cour-long (usually
comprised of twelve episodes) will likely finish airing by the start of Spring 2020, which
will begin at the start of April 2020. Some shows may begin release in special premieres
before the start of the season, but since most of the episodes air within the season, the
show is considered to premiere in that season.

Registered users on the MyAnimeList platform may add anime that they have watched or plan
to watch on their personal list. Adding anime they have watched typically entails the
attachment of an arbitrary, unitless score to that particular title. This score must be an
integer from $1$ to $10$, inclusive, where $10$ typically means that the user regards the
show as a masterpiece, and $1$, that the user regards the show as part of the lowest tier
of anime. Users may also post a review for the show describing the rationale for the score
they assign. MyAnimeList calculates and displays an aggregate score for each anime, a
decimal value rounded to two places when displayed, based off user scores, the number of
users who have scored the title, and a number of other variables [@ref_mal_score_calc].

# Data

The population considered consists of all the anime in the MyAnimeList database that
satisfy the requirements outlined below. The Jikan API [@ref_jikan_api], a public,
unofficial MyAnimeList JSON API, was queried by a script to retrieve and automatically
filter anime data from MyAnimeList. The final population set has `r nrow(fulldata)`
titles.

The data set analyzed is a simple random sample of `r nrow(data)` anime selected from the
population. For these anime, the relationship between time, the explanatory variable, and
MyAnimeList aggregate score, the response variable, is examined.

## Format

Time is considered in units of seasons. In the data, the premiere season for each show is
represented as the number of seasons since Winter 1980. For example, Spring 2011 would be
represented by the number `r (4 * 2011 + 1) - (4 * 1980)`.

The aggregate score value is the same hundredths-rounded decimal displayed on MyAnimeList.

## Requirements

\noindent
**Aggregate score** The listing must be given an aggregate score. Listings with no
aggregate scores are filtered out. MyAnimeList omits aggregate scores for anime that fail
certain requirements [@ref_mal_score_calc]. These include shows that have not yet been
released or are rated R18+.[^1]

\noindent
**Airing status** Anime that have not finished airing are not included. Scores are likely
to fluctuate as the show is airing and usually stabilize after users input their final
scores.

\noindent
**Number of scores** The listing must have been scored by 1500 or more users. This is to
include only shows exposed to a sufficiently significant audience.

## Sampling Process

Each of the anime in the population was assigned an integer identifier from $0$ to
`r nrow(data)-1` in order of MyAnimeList rank, separate from the existing MyAnimeList
database identifier. `r nrow(data)` unique integers in the range [0,`r nrow(data)-1`] were
generated using a random number generator. Those anime whose assigned identifiers matched
the generated integers were chosen to be included in the sample. The sampling process was
performed in a script.[^2]

## Limitations

Consideration of the data as a real reflection of the MyAnimeList userbase's opinion is
subject to a number of limitations.

Firstly, only the opaque aggregate score value calculated by the MyAnimeList website is
considered. The value is a weighted combination of individual scores selected by different
users who may apply varied scoring scales and criteria.

Secondly, not all users have watched and scored all the anime. Because of licensing and
availability, as well as the simple question of time, it is essentially impossible to
assume so. Therefore, each the scores will represent only a subset of all the users on
MyAnimeList.

# Analysis

```{r consts, message = FALSE, echo = FALSE}
xlbl <- "Seasons since Winter 1980"
ylbl <- "Aggregate Score"
mainsize <- 0.8
lblsize <- 1.2
axissize <- 1.2
ptsize <- 0.6
```

## Scatter Plot

All data points in the sample are plotted (see Figure \ref{scatter}). As the season value
becomes greater, representing more recent seasons, the aggregate score values become more
varied.

```{r scatterplot, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Aggregate Scores over Seasons Scatter \\label{scatter}"}
plot(x = season, y = score,
     ylim = c(floor(min(score)), 10),
     main = "", xlab = xlbl, ylab = ylbl,
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)
```

\noindent Since there exists a direct relationship between how recent the season is and
the number of anime (see Figure \ref{seasonhisto}), this is rather unsurprising. There
does not appear to be any kind of strong relationship between the two variables.

```{r season_histogram, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Frequency of Anime in Seasons \\label{seasonhisto}"}
season_range <- range(season)
hist(season,
     breaks = seq(0, season_range[2], season_range[2] / 30),
     main = "", xlab = xlbl, ylab = "Frequency",
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)
```

## Linear Model

```{r regeq, message = FALSE, echo = FALSE}
regeq <- function(summary, x) {
  slope <- summary$coefficients[2]
  yint <- summary$coefficients[1]
  return(sprintf("$\\hat{y} = %s %.3f %s %s %.3f$",
                     if (slope < 0) "" else "+",
                     slope,
                     x,
                     if (yint < 0) "" else "+",
                     yint))
}

```

```{r lin_regression, message = FALSE, echo = FALSE}
linreg <- lm(score ~ season)
linreg_summary <- summary(linreg)

linreg_slope <- linreg_summary$coefficients[2]
linreg_yint <- linreg_summary$coefficients[1]
linreg_rsq <- linreg_summary$r.squared
linreg_r <- sqrt(linreg_rsq)

linreg_eq <- regeq(linreg_summary, "x")
```

A least-squares regression line is calculated and laid over the scatter plot (see Figure
\ref{scatterlinreg}). The LSRL is represented by the equation `r linreg_eq`, where
$\hat{y}$ represents the predicted aggregate score and $x$ represents the number of
seasons since Winter 1980. The model predicts the score for anime that premiere in Winter
1980 to be `r sprintf("$%.3f$", linreg_yint)`. For every increase in the number of seasons
since Winter 1980 by $1$, the LSRL states that the aggregate MyAnimeList score will
`r if (linreg_slope < 0) "decrease" else "increase"` by
`r sprintf("$%.3f$", abs(linreg_slope))`.

```{r scatterplot_regression, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Aggregate Scores with Linear Model \\label{scatterlinreg}"}
plot(x = season, y = score,
     ylim = c(floor(min(score)), 10),
     main = "", xlab = xlbl, ylab = ylbl,
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)
abline(linreg)
```

\noindent However, the $r$ value of the model is `r sprintf("$%.3f$", linreg_r)`,
suggesting a minimal linear relationship between the MyAnimeList aggregate score and the
number of seasons since Winter 1980 and the aggregate score. The $r^2$ value is
`r sprintf("$%.3f$", linreg_rsq)`, meaning that `r sprintf("$%.3f$", 100 * linreg_rsq)`
percent of the variation in the score can be explained by the LSRL between the number of
seasons since Winter 1980 and the aggregate score; the $r^2$ value indicates a very weak
linear relationship between the two variables.

The residual plot (see Figure \ref{residuallinreg}) also suggests a weak linear
relationship; the residuals are not in uniformly random scatter around the horizon.

```{r residual_linear, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Residual Plot of Linear Model \\label{residuallinreg}"}
linreg_resid <- resid(linreg)
plot(x = season, y = linreg_resid,
     main = "", xlab = xlbl, ylab = "Residual",
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)
abline(0, 0)
```
\noindent Thus, no strong linear relationship between the variables is concluded.

## Logarithmic Model

```{r, message = FALSE, echo = FALSE}
logreg <- lm(score ~ log(season))
logreg_summary <- summary(logreg)
logreg_slope <- logreg_summary$coefficients[2]
logreg_yint <- logreg_summary$coefficients[1]
logreg_rsq <- logreg_summary$r.squared
logreg_eq <- regeq(logreg_summary, "\\ln{x}")
```

In addition to the linear model, a logarithmic model, using the transformation
$x_{new} = \ln{x}$ was calculated for the data, where $x$ is the explanatory variable. The
model is represented by the equation `r logreg_eq` (see Figure \ref{scatterlogreg}), where
$\hat{y}$ is the predicted aggregate score, suggesting that with every increase in the
value of $\ln{x}$ by $1$, the value of $\hat{y}$
`r if (logreg_slope < 0) "decreases" else "increases"` by
`r sprintf("$%.3f$", abs(logreg_slope))`. It predicts that an anime released in Winter
1980 would have a score of `r sprintf("$%.3f$", logreg_yint)`.

The model has an $r$ value of `r sprintf("$%.3f$", sqrt(logreg_rsq))` and $r^2$ value of
`r sprintf("$%.3f$", logreg_rsq)`, meaning `r sprintf("$%.3f$", 100 * logreg_rsq)` percent
of the variation in the aggregate score can be explained by the LSRL between the season
value and the aggregate score.

```{r, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Aggregate Scores with Logarithmic Model \\label{scatterlogreg}"}
plot(x = season, y = score,
     ylim = c(floor(min(score)), 10),
     main = "", xlab = xlbl, ylab = ylbl,
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)

range <- range(season)
xvals <- seq(range[1], range[2], len = length(score))
lines(xvals, predict(logreg, newdata = data.frame(xvals)))
```

\noindent The residual plot is shown in Figure \ref{residlogreg}. The residual plots for
the linear model and logarithmic model are very similar. The correlation coefficients and
coefficients of determination for both models suggest that they are both weak models.

```{r, message = FALSE, echo = FALSE, wrapf = TRUE, fig.show = 'hide', fig.cap = "Residual Plot of Logarithmic Model \\label{residlogreg}"}
logreg_resid <- resid(logreg)
plot(x = season, y = logreg_resid,
     main = "", xlab = xlbl, ylab = "Residual",
     cex.main = mainsize, cex.lab = lblsize, cex.axis = axissize,
     cex = ptsize
)
abline(0, 0)
```

## Prediction

The correlation coefficients and coefficients of determination for the two models
considered suggest that the logarithmic model is a slightly worse fit for the data.

Problematically, the data exhibits heteroskedasticity, meaning the variation in the
response variable variable is nonconstant over the values of the explanatory variable
[@ref_heteroskedasticity]. In the case of the data, the variation in the aggregate score
values increases as the value for the number of seasons since Winter 1980 increases. As
evidenced in the scatter plot, small values of the latter variable result in small scatter
in the former variable, whereas large values of the latter variable yield large scatter in
the former variable.

The presence of heteroskedasticity can be verified using the Breusch-Pagan test
[@ref_rectify_heteroskedasticity]. The test was run using the `ncvTest()` function from
the R package `car` [@ref_r_pkg_car]. The output is shown below.

```{r ncvtest}
car::ncvTest(linreg)
```

\noindent The p-value result from the chi-squared test is less than $0.05$; thus, the null
hypothesis that the data is homoskedastic is rejected and heteroskedasticity is inferred.

Because of the heteroskedastic nature of the data, the predictive accuracy of the model
likely decreases as greater explanatory variable values are used to predict the aggregate
score for anime premiering in that season. Nonetheless, an attempt will be made at using
the linear model to produce both interpolative and extrapolative aggregate score
predictions.

### Interpolative Prediction

```{r, message = FALSE, echo = FALSE}
linreg_eval <- function(x) {
  linreg_yint + linreg_slope * x
}

inter_low_x <- 2 + 1995 * 4 - (1980 * 4)
inter_low_y <-  linreg_eval(inter_low_x)
```

An interpolative prediction for the score of an anime released in Summer 1995, with $x =$
`r sprintf("$%d$", inter_low_x)`, was made. The predicted aggregate score value is
`r regeq(linreg, sprintf("(%d)", inter_low_x))` $=$ `r sprintf("$%.3f$", inter_low_y)`,
which is not too far from the scores of many anime that aired that season, though that
cannot necessarily be attributed to the accuracy of the prediction.

### Extrapolative Prediction

```{r, message = FALSE, echo = FALSE}
astro_boy_x <- 1963 * 4 - (1980 * 4)
astro_boy_y <- linreg_eval(astro_boy_x)

future_x <- 2050 * 4 - (1980 * 4)
future_y <- linreg_eval(future_x)
```

Often miscredited as the first television anime series, *Tetsuwan Atom*, more commonly
known in the English-speaking community as *Astro Boy*, premiered on January 1, 1963
[@ref_astro_boy_miscredit]. With $x =$ `r sprintf("$%d$", astro_boy_x)`, the linear model
predicts that MyAnimeList aggregate score for *Tetsuwan Atom* to be
`r regeq(linreg, sprintf("(%d)", astro_boy_x))` $=$ `r sprintf("$%.3f$", astro_boy_y)`.
*Tetsuwan Atom* has in reality garnered a lower score on the website of $7.23$.

Another data point to extrapolate is perhaps the MyAnimeList aggregate score of some title
released in the future. With $x =$ `r sprintf("$%d$", future_x)`, the model predicts that
the aggregate score for some anime premiering in Winter 2050 to be
`r regeq(linreg, sprintf("(%d)", future_x))` $=$ `r sprintf("$%.3f$", future_y)`.
However, the shape of the scatter indicates that the scores for anime in Winter 2050 would
encompass a wide range of values.

## Conclusions

One goal of the study was to examine if users in the MyAnimeList community on average have
a higher opinion of older anime---those that might be considered "classics"---than more
recent releases. While the linear model suggests a negative trend in aggregate scores over
time, the overall change over time is minimal. Furthermore, it is difficult to attribute
this strictly to MyAnimeList users' preference for anime from the 1980's and 1990's that
many might consider as classics. The limitations of the data discussed previously apply.
Particularly, it is likely and significant that newer viewers of anime have not watched at
all or as many older anime. Another important factor is that anime has become and is
becoming more mainstream, and production of it, more widepsread (and therefore having
greater variation in quality) [@ref_anime_rec_ann]; thus it makes sense that the variation
in scores increases with time.

Besides the variation in MyAnimeList aggregate score being directly proportional to the
number of seasons since Winter 1980 anime premiere in, there not does appear to be any
kind of strong relationship between the values of the explanatory and response variables.

### Further Research Possibilities

The study provided an example of data where definitive conclusions are not easy to derive
from. Further research could be done to perhaps consider and capture the sentiment of
written user reviews and other factors to more accurately examine the change in user
perceptions of anime over time.

\End{multicols}

\newpage
\newgeometry{margin=4cm}

# Appendix

## Appendix A: Scripts {#appendix-a}

### Sampling Script

The sampling script is written in Go, an open-source, general-purpose programming language
created by developers at Google [@ref_golang].

\small
\setstretch{0.8}

~~~~~~{#sample-selector .go .numberLines}
package main

import (
  "bytes"
  "encoding/csv"
  "math/rand"
  "os"
  "strconv"
  "time"
)

func main() {
  file, err := os.Open("data.csv")
  if err != nil {
    panic(err)
  }
  defer file.Close()

  r := csv.NewReader(file)

  nfile, err := os.Create("sample.csv")
  if err != nil {
    panic(err)
  }
  w := csv.NewWriter(nfile)
  defer w.Flush()

  w.Write([]string{"ID", "Title", "Rank", "Score", "ScoredBy",
    "Popularity", "Members", "Favorites", "Season", "Episodes"})

  data, err := r.ReadAll()
  if err != nil {
    panic(err)
  }
  data = data[1:]

  seed := rand.NewSource(time.Now().UnixNano())
  rng := rand.New(seed)

  max := len(data)

  for i := 0; i < 2000; i++ {
    n := rng.Intn(max)
    row := data[n]

    if len(row[8]) != 5 {
      i--
    } else {
      parts := splitSubN(row[8], 4)
      year, err := strconv.Atoi(parts[0])
      if err != nil {
        panic(err)
    }
      sn, err := strconv.Atoi(parts[1])
      if err != nil {
        panic(err)
      }

      v := (4*year + sn - 1) - (4 * 1915)
      if v < 0 {
        i--
        continue
      }
      row[8] = strconv.Itoa(v)

      w.Write(row)
    }
  }
}

func splitSubN(s string, n int) []string {
  sub := ""
  subs := []string{}

  runes := bytes.Runes([]byte(s))
  l := len(runes)
  for i, r := range runes {
    sub = sub + string(r)
    if (i+1)%n == 0 {
      subs = append(subs, sub)
      sub = ""
    } else if (i + 1) == l {
      subs = append(subs, sub)
    }
  }

  return subs
}
~~~~~~

\normalsize
\setstretch{1}

## Appendix B: Sample Data {#appendix-b}

\setstretch{0.9}

```{r data_display, echo = FALSE, message = FALSE}
df <- data.frame(ID = data$ID, Title = data$Title,
                 Score = data$Score, Season = data$Season)
trim <- function(x) gsub("^\\s+|\\s+$", "", x)
df["Title"] <- unlist(Map({
  function(s) {
    if (nchar(as.character(trim(s))) > 53) {
      s <- paste(substr(trim(s), 0, 50), "...", sep = "")
    } else {
      s <- paste(s)
    }
    s
  }
}, df$Title))


knitr::kable(df, "pandoc",
             col.names = c("ID [^3]", "Title[^4]",
                           "Score[^5]", "Season [^6]"),
             align = c("r", "l", "l", "l")
)
```

[^1]: Otherwise, the data set has not been audited to remove
    potentially questionable titles.

[^2]: See [Appendix A](#appendix-a).

[^3]: MyAnimeList database identifier.

[^4]: Titles have been truncated to 50 characters.

[^5]: MyAnimeList aggregate score.

[^6]: Number of seasons since Winter 1980.
